Operationally-Safe Peer-to-Peer Energy Trading in Distribution Grids: A Game-Theoretic Market-Clearing Mechanism

### 2022-01-07 papers/02 journal v2/journal_v14.tex
storage model changed
g

\smallskip
We consider a linear approximation of power-flow equations, which is standard in the literature of P2P markets, e.g., \cite{yang2019,moret2020}. Specifically, for each bus $y \in \mc B$, it must hold that
\begin{equation}
\sum_{i \in \mc P_y^\mathrm{b}}p_i^{\mathrm{d}}+ \sum_{i\in \mc N_y^{\mathrm b}} \left(p_i^{\mathrm d}-p_{i}^{\mathrm{di}}-\edit{p_{i}^{\mathrm{ds}}+p_{i}^{\mathrm{ch}}}\right)-p_{y}^{\mathrm{tg}}=\sum_{z\in \mc B_y}p_{(y,z)}^{\ell}, \label{eq:p_bal_p}
\end{equation}
which indicates local power balance of bus $y$, similarly to \eqref{eq:l_pow_b} although now it relates power generation, consumption and line powers. Moreover, it must hold that
\begin{subequations}
\small
\label{eq:pf_pq}
\begin{align}
&p_{(y,z)}^{\ell} = B_{(y,z)}\left({\theta_y - \theta_z} \right) - G_{(y,z)}\left(v_y - v_z \right), \, \, \forall z \in \mc B_y, \label{eq:pf_p}\\
&q_{(y,z)}^{\ell} = G_{(y,z)}\left({\theta_y - \theta_z} \right) + B_{(y,z)}\left(v_y - v_z \right), \, \,  \forall z \in \mc B_y, \label{eq:pf_q}
\end{align}
\label{eq:pf_all}
\end{subequations}
which represent the power flow equations of line $(y,z)$ from the perspective of bus $y$, with $B_{(y,z)}$ and  $G_{(y,z)}$ denoting the susceptance and conductance, respectively, of line $(y,z)$. Note that by \eqref{eq:pf_p} and \eqref{eq:pf_q}, for each pair $(y,z) \in \mc L$, it holds that $p_{(y,z)}^{\ell} = {-p}_{(z,y)}^{\ell}$ and $q_{(y,z)}^{\ell} = {-q}_{(z,y)}^{\ell}$.

@@

%\begin{definition}[Extended P2P market model]
%\label{def:p2p_ext}
\section{A Distributed Market-clearing Mechanism}
\label{sub:alg}
	By letting the decision variables related to the physical constraints handled by a DNO (agent $N+1$ in the game), the P2P market model can be compactly written as the problem of finding $u_i^*$ in \eqref{eq:locOpt}, for all $i \in \mc N^+$, where the decision variable $u_i$ is defined as
$$u_i \hspace{-2pt} = \hspace{-2pt}\begin{cases} \col\hspace{-2pt}\left(p_{i}^{\mathrm{di}},\edit{p_{i}^{\mathrm{ch}},p_{i}^{\mathrm{ds}}, } p_{i}^{\mathrm{mg}},\{p_{(i,j)}^{\mathrm {tr}}\}_{j\in \mc N_i}\right)\hspace{-2pt}, \ \qquad \qquad \; \; \forall  i \in \mc N,\\
	\col\hspace{-2pt}\left(\{\theta_y, v_y, p_y^{\mathrm{tg}},\{p_{(y,z)}^{\ell},q_{(y,z)}^{\ell}\}_{z \in \mc B_y} \}_{y\in\mc B} \right)\hspace{-2pt},   i\!=\! N\!+\!1;
	\end{cases}$$ 
the cost function is defined as
	\begin{multline}
	J_i(u_i,u_{-i}) =
f_{i}^{\mathrm{di}}(p_{i}^{\mathrm{di}}) + f_{i}^{\mathrm{st}}(\edit{p_{i}^{\mathrm{ch}},p_{i}^{\mathrm{ds}}})+ f_{i}^{\mathrm{tr}} \left( \{ p_{(i,j)}^{\mathrm{tr}} \}_{j \in \mc N_i} \right)\\
    + f_{i}^{\mathrm{mg}}\left( p_{i}^{\mathrm{mg}},\sigma^{\textrm{mg}} \right), \quad \forall  i \in \mc N,
 \label{eq:cost_def}
	\end{multline}
whereas\footnote{Here, we assume that the DNO does not have preferences on the outcome, provided that it is a feasible solution for the network.} $J_{N+1}=0$; the local action set is
\begin{align}
\label{eq:constr_def}
\mc U_i =
\left\{
\begin{array}{l r}
\left\{u_i \,|~ \text{\eqref{eq:p_dg_bound}, \eqref{eq:x}, \eqref{eq:l_pow_b}, \eqref{eq:p_t_bound} hold} \, \right\}, & \forall i \in \mc N, \\
\left\{ u_i \,|~ \text{\eqref{eq:pf_pq},\eqref{eq:line}, \eqref{eq:grid_ex} hold} \,\right\}, & i\!=\!N\!+\!1;
\end{array}
\right.
\end{align}
and finally, the set of coupling constraints is 
\begin{equation}
\label{eq:Cconstr_def}
\mc C = \left\{
u~|~ \text{\eqref{eq:rep_const}, \eqref{eq:p_mg_bound}, \eqref{eq:p_bal_p}, \eqref{eq:grid_const2} hold}
\right\}.
\end{equation}

@@

\smallskip 
The proposed market-clearing algorithm is summarized in Algorithm~1 and its information flow is illustrated in Fig.~\ref{fig:IFC}. 
%, while the step-size choices therein are formalized next.
%\smallskip
%\begin{assumption}\label{ass:SSS}
%The step sizes in Alg.~1 are set as follows:
%\begin{enumerate}[(i)]
%\item $\forall i \!\in \!\mc N$: $\alpha_i \!<\! 
%3 +N \underset{h\in \mc H}{\max} d_h^{\text{mg}} $, $\beta^{\text{tr}}_{(i,j)}\! =\! \beta^{\text{tr}}_{ (j,i)} \!<\! \frac{1}{2}$, $\forall j \!\in\! \mc N_i$. 
%
%\item $\alpha_{N+1} <2$, $\gamma^{\text{mg}} < \frac{1}{N}$, $\beta^{\text{tg}} < (|\mc N| + |\mc B|)^{-1}$ and $\beta_y^{\text{pb}} < (1+2|\mc N_y^{\mathrm{b}}|+|\mc B_y|)^{-1}$, for all $y \in \mc B$.
%{\hfill $\square$}
%\end{enumerate}
%\end{assumption}
%\smallskip
The next proposition shows its global convergence of Algorithm~1 to a variational\footnote{Variational GNEs (v-GNEs) are  a special subclass of GNEs that enjoys the property of ``economic fairness”, namely, the marginal loss due to the presence of the coupling constraints is the same for each
agent, and coincides with the solutions to a specific variational inequality \cite{kulkarni2012variational}.} GNE of the P2P market game. %The algorithm derivation and its convergence analysis are discussed in Appendix \ref{app:CA}.

@@

\begin{figure}[t]
\centering
\includegraphics[width=.5\textwidth]{figures/algorithm1_GB_v4}
\caption{Information flow of Algorithm~1 for each prosumer $i \in \mc N$ (top boxes) and the DNO (bottom box).}
\label{fig:IFC}
\end{figure}

\smallskip

%%%%%%%%
\algblockdefx[init]{init}{Endinit}
[1][<default value>]{\textbf{Initialization}}
[2][<default value>]{\textbf{end initialization}}

\algblockdefx[DNO]{DNO}{EndDNO}
[1][<default value>]{\textbf{DNO routine}}
[2][<default value>]{\textbf{end DNO routine}}

\algblockdefx[PRO]{PRO}{EndPRO}
[1][<default value>]{\textbf{Prosumer $i$ routine}}
[2][<default value>]{\textbf{end prosumer $i$ routine}}

\algblockdefx[Primal]{Primal}{EndPrimal}
[1][<default value>]{\textbf{primal update}}
[2][<default value>]{\textbf{end}}

\algblockdefx[Dual]{Dual}{EndDual}
[1][<default value>]{\textbf{dual update}}
[2][<default value>]{\textbf{end}}

\algblockdefx[Aux]{Aux}{EndAux}
[1][<default value>]{\textbf{auxiliary update}}
[2][<default value>]{\textbf{end}}

\algblockdefx[Comm]{Comm}{EndComm}
[1][<default value>]{\textbf{communication}}
[2][<default value>]{\textbf{end communication}}

\algblockdefx[Agg]{Agg}{EndAgg}
[1][<default value>]{\textbf{aggregation update}}
[2][<default value>]{\textbf{end}}

\algblockdefx[IUC]{IUC}{EndIUC}
[1][<default value>]{\textbf{While convergence is not achieved do:}}
[2][<default value>]{\textbf{end while}}
%%%%%%%%%%

\begin{algorithm*}[htbp]
\caption{Distributed P2P Markets Clearing Mechanism \red{[check modification because of extra variables of charging and discharging]}}
\label{alg:alg1}
\begin{algorithmic}[1]
\small

\init{ }
\State
\textbf{Prosumers.} For all $i \in \mc N$: set $u_i(0) \in \mc U_i$, $\mu^{\text{tr}}_{(i,j)}(0) = \0$, $\forall j \in \mc N_i$; $\alpha_i \!<\! 
\red{3} +N \underset{h\in \mc H}{\max} d_h^{\text{mg}} $, $\beta^{\text{tr}}_{(i,j)}\! =\! \beta^{\text{tr}}_{ (j,i)} \!<\! \frac{1}{2}$, $\forall j \!\in\! \mc N_i$.
\State
\textbf{DNO.} Set $u_{N+1}(0) \!\in\! \mc U_{N+1}$, $\lambda^{\text{mg}}\!=\!\0$, $\mu^{\text{tg}} \!=\! \0$, $\mu_y^{\text{pb}}(0)\! = \!\0$, $\forall y \!\in\! \mc B$; $\alpha_{N+1} \!<\!2$, $\gamma^{\text{mg}} \!<\! \frac{1}{N}$, $\beta^{\text{tg}}\! <\! \frac{1}{|\mc N| \!+\! |\mc B|}$, $\beta_y^{\text{pb}} \!<\! \frac{1}{1\!+\!2|\mc N_y^{\mathrm{b}}|\!+\!|\mc B_y|}$,  $\forall y\!\in\! \mc B $.%

\Endinit

\smallskip
\IUC{ }
\smallskip
\ForAll{$ i \in \mc N$}
\PRO{ }
\Primal{ }
\Comment{$u_i = \{$generation, storage, main grid, trades$\}$}

\smallskip
\State 
$\psi_i(k) = 
	\col \Big(-\mu_y^{\text{pb}}(k),-\mu_y^{\text{pb}}(k), \edit{-\mu_y^{\text{pb}}(k),}
	{
	%\left(
	\left[
	\begin{smallmatrix}
	I_H\\
	- I_H 
	\end{smallmatrix}
	\right] 
	%\otimes I_H
%\right)	
	}^\top \lambda^{\text{mg}}(k) + \mu^{\text{tg}}(k),
	%
	\left\{ {\mu^{\text{tr}}_{(i,j)}(k)}\right\}_{j \in \mc N_i}   \Big)$
\Comment{auxiliary vector}

\State
$u_i(k+1)   =
\left\{
\begin{array}{r l}
	\underset{\xi \in \R^{n_i}}{\argmin} & 
	\tilde J_{i} \big( \xi, \sigma^{\text{mg}}(k) \big) 
	+ {\psi_i(k)}^\top \xi + \frac{1}{2 \alpha_i}
	\left\| \xi - u_i(k) 
	\textstyle
	  \right\|^2 \\
	\text{s.t. } & \xi \in \mc U_i
\end{array} 
	\right.	$
\Comment{quadratic programming}	
\EndPrimal

\Comm{ (to DNO and trading partners)}
\State $\eta_i(k+1)= p^{\text{d}}_i-p^{\text{di}}_i(k+1)\edit{- p^{\text{ds}}_i(k+1)+p^{\text{ch}}_i(k+1)}$
\Comment{auxiliary vector: local load unbalance}
\State
$
p^{\textrm{mg}}_{i}(k+1), \eta_i(k+1)  \longrightarrow  \text{DNO,}
$
\Comment{forward to DNO}
     \ForAll{prosumer $ j \in \mc N_i$}

\State
 $p^{\text{tr}}_{(i,j)}(k+1)
	\longrightarrow \text{prosumer }j$
	\Comment{forward trade estimate to prosumer $j$}
	\EndFor
\EndComm

\Dual{ }
\Comment{reciprocity constraints}
\ForAll{$ j \in \mc N_i$}
\State
$\zeta^{\text{tr}}_{(i,j)}(k+1)  =  p^{\textrm{tr}}_{(i,j)} (k+1) + p^{\textrm{tr}}_{(j,i)} (k+1)$
\Comment{auxiliary vector}
\State
$\mu^{\text{tr}}_{(i,j)}(k+1) = \mu^{\text{tr}}_{(i,j)}(k) + \beta_{(i,j)}^{\text{tr}} \left( 
	2  \zeta^{\text{tr}}_{(i,j)}(k+1) - \zeta^{\text{tr}}_{(i,j)}(k)
	\right)$
	\Comment{reflected dual ascent}
\EndFor

\EndDual

\EndPRO

\EndFor

%%%%%%%%%%%%%%%%%%%%%%
\smallskip
%\Statex
\DNO{ }
%\State
%Iterate

\Primal{}
\Comment{angles, voltages, power on grid and buses}
\State
$\psi_{N+1}(k) = \col \left( 
	\left\{
	\0,\0,-\mu^{\text{tg}}(k) - \mu_y^{\text{pb}}(k), 
	\{ -\mu_y^{\text{pb}}(k), \0 \}_{z \in \mc B_y}
	\right\}_{y \in \mc B}
	\right)$
\Comment{auxiliary vector}

\State 	$u_{N+1}(k+1) = \proj_{\mc U_{N+1}}  \left( u_{N+1}(k) - (\alpha_{N+1})^{-1} \psi_{N+1}(k) \right)$
%\Comment{ solved via Algorithm 2 (see Appendix)}
\EndPrimal

%---------------------------Aggregation
\Agg{}
\State
$ \sigma^{\text{mg}}(k+1) = \sum_{i \in \mc N} p_i^{\text{mg}}(k+1) $
\Comment{aggregate active load, eqn. (10)}
\State
$\sigma^{\text{tg}}(k+1) = \sum_{y \in \mc B} p_y^{\text{tg}}(k+1)$
\Comment{aggregate grid-to-buses power }
\EndAgg

%---------------------------Dual Update
\Dual{}
\State
$\eta_{N+1}(k+1	) = 
	\left[
	\begin{smallmatrix}
	1\\
	- 1 
	\end{smallmatrix}
	\right] \otimes (2 \sigma^{\text{mg}}(k+1)- \sigma^{\text{mg}}(k)) 
	-
	\left[
	\begin{smallmatrix}
	\overline{p}^{\mathrm{mg}}\1_{H}-b \\
	-     \underline{p}^{\mathrm{mg}} \1_{H}+b
	\end{smallmatrix} 
	\right]  $
	\Comment{auxiliary vector}
	\State
$\lambda^{\text{mg}}(k+1) = \textstyle
	\proj_{\R^{2 H}_{\geq 0}}\left( 
	\lambda^{\text{mg}}(k) + \gamma^{\text{mg}} \eta_{N+1}(k+1)
	 \right)$
		\Comment{grid constraints}

\ForAll{buses $ y \in \mc B$}

\State
$\zeta^{\text{pb}}_y(k+1)   = \sum_{i \in \mc P_y^{\mathrm{b}}} p_i^{\mathrm{d}} + \sum_{i \in \mc N_y^{\mathrm{b}}} \eta_i(k+1)- p^{\text{tg}}_y(k+1) - \sum_{z \in \mc B_y} p^\ell_{(y,z)} (k+1)$
\Comment{auxiliary vector}

\State
$\mu_y^{\text{pb}}(k+1) = \mu_y^{\text{pb}}(k) + \beta^{\text{pb}}_y (2 \zeta^{\text{pb}}_y(k+1)- \zeta^{\text{pb}}_y(k))$
\Comment{local power balance of bus $y$}
\EndFor

\State
$\zeta^{\text{tg}}(k+1) = \sigma^{\text{mg}}
	(k+1)+b- \sigma^{\text{tg}}(k+1)$
\Comment{auxiliary vector}

\State
$\mu^{\text{tg}}(k+1) = \mu^{\text{tg}}(k) + \beta^{\text{tg}} (2\zeta^{\text{tg}}(k+1)-\zeta^{\text{tg}}(k))$
\Comment{grid-to-buses constraints}
\EndDual

\Comm{ (broadcast to all prosumers)}
\State
$ \{ \sigma^{\mathrm{mg}}(k+1)+b, \, \lambda^{\text{mg}}(k+1), \mu^{\text{tg}}(k+1) \} 
	\longrightarrow  \mc N$
\ForAll{buses $ y \in \mc B$}
\State
$\mu^{\text{pb}}_y(k+1)\longrightarrow \mc N_y^{\mathrm{b}}$
\Comment{only to prosumers on bus $y$}
\EndFor

\EndComm

\EndDNO

\EndIUC

\end{algorithmic}
\end{algorithm*}

@@

%\input{appendix}

>>>>

\smallskip
We consider a linear approximation of power-flow equations, which is standard in the literature of P2P markets, e.g., \cite{yang2019,moret2020}. Specifically, for each bus $y \in \mc B$, it must hold that
\begin{equation}
\sum_{i \in \mc P_y^\mathrm{b}}p_i^{\mathrm{d}}+ \sum_{i\in \mc N_y^{\mathrm b}} \eta_i - p_{y}^{\mathrm{tg}}=\sum_{z\in \mc B_y}p_{(y,z)}^{\ell}, \label{eq:p_bal_p}
\end{equation}
where $\eta_i$ is the local power unbalance of prosumer $i$, i.e.,
\begin{equation}
\label{eq:etai}
\eta_i := p_i^{\mathrm d}-p_{i}^{\mathrm{di}}-\edit{p_{i}^{\mathrm{ds}}+p_{i}^{\mathrm{ch}}}.
\end{equation}
Equation \eqref{eq:p_bal_p} represents the local power balance of bus $y$, similarly to \eqref{eq:l_pow_b} although now it relates power generation, consumption and line powers. Moreover, it must hold that
\begin{subequations}
\small
\label{eq:pf_pq}
\begin{align}
&p_{(y,z)}^{\ell} = B_{(y,z)}\left({\theta_y - \theta_z} \right) - G_{(y,z)}\left(v_y - v_z \right), \, \, \forall z \in \mc B_y, \label{eq:pf_p}\\
&q_{(y,z)}^{\ell} = G_{(y,z)}\left({\theta_y - \theta_z} \right) + B_{(y,z)}\left(v_y - v_z \right), \, \,  \forall z \in \mc B_y, \label{eq:pf_q}
\end{align}
\label{eq:pf_all}
\end{subequations}
which represent the power flow equations of line $(y,z)$ from the perspective of bus $y$, with $B_{(y,z)}$ and  $G_{(y,z)}$ denoting the susceptance and conductance, respectively, of line $(y,z)$. Note that by \eqref{eq:pf_p} and \eqref{eq:pf_q}, for each pair $(y,z) \in \mc L$, it holds that $p_{(y,z)}^{\ell} = {-p}_{(z,y)}^{\ell}$ and $q_{(y,z)}^{\ell} = {-q}_{(z,y)}^{\ell}$.

@@

%\begin{definition}[Extended P2P market model]
%\label{def:p2p_ext}
\section{A Distributed Market-clearing Mechanism}
\label{sub:alg}
	By letting the decision variables related to the physical constraints handled by a DNO (agent $N+1$ in the game), the P2P market model can be compactly written as the problem of finding $u_i^*$ in \eqref{eq:locOpt}, for all $i \in \mc N^+$, where the decision variable $u_i$ is defined as
$$u_i \hspace{-2pt} = \hspace{-2pt}\begin{cases} \col\hspace{-2pt}\left(p_{i}^{\mathrm{di}},\edit{p_{i}^{\mathrm{ch}},p_{i}^{\mathrm{ds}}, } p_{i}^{\mathrm{mg}},\{p_{(i,j)}^{\mathrm {tr}}\}_{j\in \mc N_i}\right)\hspace{-2pt}, \ \qquad \qquad \;  \forall  i \in \mc N,\\
	\col\hspace{-2pt}\left(\{\theta_y, v_y, p_y^{\mathrm{tg}},\{p_{(y,z)}^{\ell},q_{(y,z)}^{\ell}\}_{z \in \mc B_y} \}_{y\in\mc B} \right)\hspace{-2pt},  \; \quad i\!=\! N\!+\!1;
	\end{cases}$$ 
the cost function is defined as
	\begin{multline}
	J_i(u_i,u_{-i}) =
f_{i}^{\mathrm{di}}(p_{i}^{\mathrm{di}}) + f_{i}^{\mathrm{st}}(\edit{p_{i}^{\mathrm{ch}},p_{i}^{\mathrm{ds}}})+ f_{i}^{\mathrm{tr}} \left( \{ p_{(i,j)}^{\mathrm{tr}} \}_{j \in \mc N_i} \right)\\
    + f_{i}^{\mathrm{mg}}\left( p_{i}^{\mathrm{mg}},\sigma^{\textrm{mg}} \right), \quad \forall  i \in \mc N,
 \label{eq:cost_def}
	\end{multline}
whereas\footnote{Here, we assume that the DNO does not have preferences on the outcome, provided that it is a feasible solution for the network.} $J_{N+1}=0$; the local action set is
\begin{align}
\label{eq:constr_def}
\mc U_i =
\left\{
\begin{array}{l r}
\left\{u_i \,|~ \text{\eqref{eq:p_dg_bound}, \eqref{eq:x}, \eqref{eq:l_pow_b}, \eqref{eq:p_t_bound} hold} \, \right\}, & \forall i \in \mc N, \\
\left\{ u_i \,|~ \text{\eqref{eq:pf_pq},\eqref{eq:line}, \eqref{eq:grid_ex} hold} \,\right\}, & i\!=\!N\!+\!1;
\end{array}
\right.
\end{align}
and finally, the set of coupling constraints is 
\begin{equation}
\label{eq:Cconstr_def}
\mc C = \left\{
u~|~ \text{\eqref{eq:rep_const}, \eqref{eq:p_mg_bound}, \eqref{eq:p_bal_p}, \eqref{eq:grid_const2} hold}
\right\}.
\end{equation}

@@

\smallskip 
The proposed market-clearing algorithm is summarized in Algorithm~1 and its information flow is illustrated in Fig.~\ref{fig:IFC}. 
%, while the step-size choices therein are formalized next.
%\smallskip
%\begin{assumption}\label{ass:SSS}
%The step sizes in Alg.~1 are set as follows:
%\begin{enumerate}[(i)]
%\item $\forall i \!\in \!\mc N$: $\alpha_i \!<\! 
%3 +N \underset{h\in \mc H}{\max} d_h^{\text{mg}} $, $\beta^{\text{tr}}_{(i,j)}\! =\! \beta^{\text{tr}}_{ (j,i)} \!<\! \frac{1}{2}$, $\forall j \!\in\! \mc N_i$. 
%
%\item $\alpha_{N+1} <2$, $\gamma^{\text{mg}} < \frac{1}{N}$, $\beta^{\text{tg}} < (|\mc N| + |\mc B|)^{-1}$ and $\beta_y^{\text{pb}} < (1+2|\mc N_y^{\mathrm{b}}|+|\mc B_y|)^{-1}$, for all $y \in \mc B$.
%{\hfill $\square$}
%\end{enumerate}
%\end{assumption}
%\smallskip
The next proposition shows its global convergence to a variational\footnote{Variational GNEs (v-GNEs) are  a special subclass of GNEs that enjoys the property of ``economic fairness”, namely, the marginal loss due to the presence of the coupling constraints is the same for each
agent, and coincides with the solutions to a specific variational inequality \cite{kulkarni2012variational}.} GNE of the P2P market game. %The algorithm derivation and its convergence analysis are discussed in Appendix \ref{app:CA}.

@@

%\begin{figure}[t]
%\centering
%\includegraphics[width=.5\textwidth]{figures/algorithm1_GB_v4}
%\caption{Information flow of Algorithm~1 for each prosumer $i \in \mc N$ (top boxes) and the DNO (bottom box).}
%\label{fig:IFC}
%\end{figure}

\begin{figure}
\medskip \noindent
\begin{minipage}{\columnwidth}
\hrule
\smallskip
\textsc{Algorithm 1}. Semi-decentralized P2P market clearing
\smallskip
\hrule 
\smallskip
\text{Initialization}: For all prosumers $i \in \mc N$: set $\mu^{\text{tr}}_{(i,j)}(-1) = 0$, $\forall j \in \mc N_i$. DNO: set $\lambda^{\text{mg}}(0)\!=\!0$, $\mu^{\text{tg}}(0) \!=\! 0$, $\mu_y^{\text{pb}}(0)\! = \!0$, $\forall y \!\in\! \mc B$.

\medskip
 \text{Iterate until convergence $(k = 0,1,\ldots)$}
\begin{align*}
& \text{For all prosumers $i \in \mc I$ (in parallel):}\\
\quad &\left|
\begin{array}{l}
\text{Local update via \textsc{Algorithm 2}:}\\
\left|
\begin{array}{l}
\text{Set $\{\mu_{(i,j)}(k)\}_{j \in \mc N_i}$ as in \textsc{Alg. 2} (i)}\\
\text{Set $u_i(k\!+\!1)$ as in \textsc{Alg. 2} (ii)}
\end{array}
\right.\\[1em]
 \text{Communication}\\
 \left|
\begin{array}{l}
\eta_i(k\!+\!1), \; p_i^{\text{mg}}(k\!+\!1) \rightarrow \text{ DNO}\\[.5em]
\text{For all trading partners } j \in \mc N_i \text{ (in parallel):}\\
 \left|
\begin{array}{l}
p_{(i,j)}^{\text{tr}}(k\!+\!1) \rightarrow \text{ prosumer } j
\end{array}
\right.
\end{array}
\right.
\end{array}
\right.\\[.5em]
%%%
% DNO
%%%
& \text{DNO}\\
\quad &\left|
\begin{array}{l}
\text{Central update via \textsc{Algorithm 3}:}\\
\left|
\begin{array}{l}
\text{Set $u_{N+1}(k\!+\!1)$ as in \textsc{Alg. 3} (i)}\\
\text{Set $\lambda^{\text{mg}}$, $\mu^{\text{tg}}$, $\{ \mu_y^{\text{pb}}(k\!+\!1)\}_{y \in\mc B}$ as in \textsc{Alg. 3} (ii)}
\end{array}
\right.\\[1em]
\text{Communication (Gather \& Broadcast)}\\
 \left|
\begin{array}{l}
\sigma^{\mathrm{mg}},\, \lambda^{\text{mg}}, \mu^{\text{tg}}(k\!+\!1) \rightarrow \text{ all prosumers } i \in \mc N\\[.5em]
\text{For all busses } y \in \mc B \text{ (in parallel):}\\
 \left|
\begin{array}{l}
\mu_y^{\text{pb}}(k+1) \rightarrow \text{ all prosumers } i \in \mc N_y^{\text{b}}%
\end{array}%
\right.%
\end{array}%
\right.\\[1em]
\end{array}%
\right.%
\end{align*}
\smallskip
\hrule
\end{minipage}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\medskip \noindent
\begin{minipage}{\columnwidth}
\hrule
\smallskip
\textsc{Algorithm 2}. Prosumer $i$ local update
\smallskip
\hrule 
\smallskip

\text{Step sizes}: set $
 \alpha_i \!<\! 
({3} +N \max_{h}\, d_h^{\text{mg}})^{-1}$, $\beta^{\text{tr}}_{(i,j)}\! =\! \beta^{\text{tr}}_{ (j,i)} \!<\! \frac{1}{2}$.

\smallskip
\noindent 
(i) \text{Dual update:}\\[.2em]
\hspace*{.15em}
$
\left| 
\begin{array}{l}
\text{For all } j \in \mc N_i \text{ (in parallel):}\\
\left|
\begin{array}{l}
%\text{Receive } p^{\textrm{tr}}_{(j,i)} (k) \text{ from prosumer } j\\
\zeta^{\text{tr}}_{(i,j)}(k)  =  p^{\textrm{tr}}_{(i,j)} (k) + p^{\textrm{tr}}_{(j,i)} (k)\\
\mu^{\text{tr}}_{(i,j)}(k) = \mu^{\text{tr}}_{(i,j)}(k) + \beta_{(i,j)}^{\text{tr}} \left( 
	2  \zeta^{\text{tr}}_{(i,j)}(k) - \zeta^{\text{tr}}_{(i,j)}(k\!-\!1)
	\right)
\end{array}
\right.
\end{array}
\right.
$

\medskip
\noindent
(ii) \text{Primal update:}\\[.2em]
\hspace*{.15em}
$
\left| 
\begin{array}{l}
%\text{Receive } \sigma^{\mathrm{mg}}(k),\, \lambda^{\text{mg}}(k), \mu^{\text{tg}}(k), \mu_y^{\text{pb}}(k) \text{ from the DNO}\\
\psi_i(k) = 
	\alpha_i \col \Big(-\mu_y^{\text{pb}}(k),\edit{\mu_y^{\text{pb}}(k), -\mu_y^{\text{pb}}(k),}\\
	\hspace*{4em}
	{
	\left[
	\begin{smallmatrix}
	I_H\\
	- I_H 
	\end{smallmatrix}
	\right] 	
	}^\top \lambda^{\text{mg}}(k) + \mu^{\text{tg}}(k),
	%
	\left\{ {\mu^{\text{tr}}_{(i,j)}(k)}\right\}_{j \in \mc N_i}   \Big)\\[1em]
%
\text{Set } u_i(k\!+\!1) \text{ as the unique solution to}\\[.3em]
\left\{
\begin{array}{r l}
	\underset{\xi \in \R^{n_i}}{\argmin} & 
	\tilde J_{i} \big( \xi, \sigma^{\text{mg}}(k) \big) 
	+ \frac{1}{2 \alpha_i}
	\left\| \xi - u_i(k) +  \psi_i(k) 
	\textstyle
	  \right\|^2 \\
	\text{s.t. } & \xi \in \mc U_i
\end{array} 
\right.
\end{array}
\right.
$

\smallskip
\hrule
\end{minipage}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}
\medskip \noindent
\begin{minipage}{\columnwidth}
\hrule
\smallskip
\textsc{Algorithm 3}. DNO central update
\smallskip
\hrule 
\smallskip

\text{Step sizes}: set $\alpha_{N+1} <2$, $\gamma^{\text{mg}} < 1/N$, $\beta^{\text{tg}} < (|\mc N| \!+\! |\mc B|)^{-1}$, and $\beta_y^{\text{pb}} < (1\!+\!2|\mc N_y^{\mathrm{b}}|\!+\!|\mc B_y|)^{-1}$,  for all busses $y\!\in\! \mc B $.

\smallskip
\noindent 
(i) \text{Primal update:}\\[.2em]
\hspace*{.15em}
$
\left| 
\begin{array}{l}
%\text{Receive } \\
\psi(k) \!=\!\col \Big( 
	\left\{
	\0,\mu^{\text{tg}}(k) + \mu_y^{\text{pb}}(k), 
	\{ \mu_y^{\text{pb}}(k), \0 \}_{z \in \mc B_y}
	\right\}_{y \in \mc B} \Big)\\[.7em]
%
u_{N+1}(k+1) = \proj_{\mc U_{N+1}}  \left( u_{N+1}(k) + (\alpha_{N+1})^{-1} \psi(k) \right)
\end{array}
\right.
$

\medskip
\noindent
\noindent 
(ii) \text{Dual update:}\\[.2em]
\hspace*{.15em}
$
\left| 
\begin{array}{l}
%
\eta(k\!+\!1) = 
	\left[
	\begin{smallmatrix}
	1\\
	- 1 
	\end{smallmatrix}
	\right] \otimes (2 \sigma^{\text{mg}}(k\!+\!1)- \sigma^{\text{mg}}(k)) 
	-
	\left[
	\begin{smallmatrix}
	\overline{p}^{\mathrm{mg}}\1_{H}-b \\
	-     \underline{p}^{\mathrm{mg}} \1_{H}+b
	\end{smallmatrix} 
	\right]\\
	% lambda update
	\lambda^{\text{mg}}(k+1) = \textstyle
	\proj_{\R^{2 H}_{\geq 0}}\left( 
	\lambda^{\text{mg}}(k) + \gamma^{\text{mg}} \eta(k\!+\!1)
	 \right)\\
%
\zeta^{\text{tg}}(k+1) = \sigma^{\text{mg}}
	(k\!+\!1)+b- \sigma^{\text{tg}}(k\!+\!1)\\
	%
	\mu^{\text{tg}}(k+1) = \mu^{\text{tg}}(k) + \beta^{\text{tg}} (2\zeta^{\text{tg}}(k+1)-\zeta^{\text{tg}}(k))\\[.5em]
	%
\text{For all busses } y \in \mc B \text{ (in parallel):}\\
\left|
\begin{array}{l}
%\text{Receive } p^{\textrm{tr}}_{(j,i)} (k) \text{ from prosumer } j\\
\zeta^{\text{pb}}_y(k+1)   = \sum_{i \in \mc P_y^{\mathrm{b}}} p_i^{\mathrm{d}} + \sum_{i \in \mc N_y^{\mathrm{b}}} \eta_i(k\!+\!1)\\
\hspace*{8em} - p^{\text{tg}}_y(k\!+\!1) - \sum_{z \in \mc B_y} p^\ell_{(y,z)} (k\!+\!1)\\
%
\mu_y^{\text{pb}}(k+1) = \mu_y^{\text{pb}}(k) + \beta^{\text{pb}}_y (2 \zeta^{\text{pb}}_y(k\!+\!1)- \zeta^{\text{pb}}_y(k))
\end{array}
\right.
\end{array}
\right.
$

\smallskip
\hrule
\end{minipage}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\include{appendix}
